Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-13 doc/JFLA2022/paper.tex
fix typos

Unfortunately, the examples  most commonly shown in the litterature
(see for instance~\cite{KP82, bauer2008, BauerHydra}) 
assume that the hydra grows $k$ copies at step $k$ of the game, which is incompatible with our proof.
We prove now that Theorem~\ref{thm3} still holds with these typical battles.
%by borrowing new combinatorial results from~\cite{KS81}.
Since we are looking  for a minoration of the length of such battles,
we can work with the following hypotheses and invariants, 
without any loss of generality.

@@

\Hydras wants to be a bridge between scientific litterature (\emph{e.g.}~\cite{KP82, KS81, schutte} and proof assistant technology. For the mathematician, it may give a concrete view of the mathematical content, not only through full proofs, but also through significative computations: examples, functions associated with constructive proofs, etc. For the \coq learner, it provides a consistent set of examples,
allowing to present and compare various formalization and proving techniques. %It may be also used as a library, through opam packages.
It is also a medium sized library (more than 50K LOC), dependent on various tools and libraries of the \coq ecosystem, which  may be also used to experiment new techniques of continuous maintenance of the code and its documentation.

>>>>

Unfortunately, the examples  most commonly shown in the literature
(see for instance~\cite{KP82, bauer2008, BauerHydra}) 
assume that the hydra grows $k$ copies at step $k$ of the game, which is incompatible with our proof.
We prove now that Theorem~\ref{thm3} still holds with these typical battles.
%by borrowing new combinatorial results from~\cite{KS81}.
Since we are looking  for a minoration of the length of such battles,
we can work with the following hypotheses and invariants, 
without any loss of generality.

@@

\Hydras wants to be a bridge between scientific literature (\emph{e.g.}~\cite{KP82, KS81, schutte} and proof assistant technology. For the mathematician, it may give a concrete view of the mathematical content, not only through full proofs, but also through significative computations: examples, functions associated with constructive proofs, etc. For the \coq learner, it provides a consistent set of examples,
allowing to present and compare various formalization and proving techniques. %It may be also used as a library, through opam packages.
It is also a medium sized library (more than 50K LOC), dependent on various tools and libraries of the \coq ecosystem, which  may be also used to experiment new techniques of continuous maintenance of the code and its documentation.
